Coordinated shifts in allocation among reproductive tissues across 14 coexisting plant species

### 2017-02-14 Analysis-accessory.Rmd
work on supplementary material for Accessory ms. Added metadata files for several data files, worked on figures for SuppMaterial.
work on Accessory manuscript - Supplementary Information should currently compile. Tables should be final (other than sequence). Small amount more worked needed in descriptions at beginning.
next version of manuscript complete except very end of Intro

@@

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=1)
results <- lines(fit$groupsummary)
plot(fit,xlab=xvar,ylab=yvar,pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
results
```

@@

plot(repro_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$repro_costs,SummarySpp[["se"]]$accessory_costs)
slopes <- sma(repro_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,lty=2)
summary(slopes)

plot(prop_pollen_attract_vs_all_repro_all_repro~ seedset,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5)

@@

plot(success_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="seed costs (mg/seed)",xlab="",cex=1.5)
y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$success_costs,SummarySpp[["se"]]$success_costs)
slopes <- sma(success_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,lty=2)
acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

plot(pollen_attract_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["se"]]$pollen_attract_costs)
slopes <- sma(pollen_attract_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,lty=2)
acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

plot(provisioning_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
slopes <- sma(provisioning_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,lty=2)
y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$provisioning_costs,SummarySpp[["se"]]$provisioning_costs)
acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)

plot(discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="all discarded costs (mg/seed)",xlab="",cex=1.5)
slopes <- sma(discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,lty=2)
y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$discarded_costs,SummarySpp[["se"]]$discarded_costs)
acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

plot(prepollen_all_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="all pre-pollination costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prepollen_all_costs,SummarySpp[["se"]]$prepollen_all_costs)
slopes <- sma(prepollen_all_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,lty=2)
acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

plot(prepollen_discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted pre-pollination costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prepollen_discarded_costs,SummarySpp[["se"]]$prepollen_discarded_costs)
slopes <- sma(prepollen_discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,lty=2)
acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

plot(postpollen_aborted_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted during provisioning costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$postpollen_aborted_costs,SummarySpp[["se"]]$postpollen_aborted_costs)
slopes <- sma(postpollen_aborted_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,lty=2)
acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

acc_by_species$variable = c("total accessory costs","seed costs","pollen attraction costs","provisioning costs", "failed tissues costs","all pre-pollen costs per seed","failed pre-pollination costs","failed provisioning costs")

@@

#Figure 01. predictions
```{r}
png("ms/Accessory/output/Figure01b&c&d_predictions.png", height=3.6, width=9, units="in", res=300)
par(mfrow=c(1,3), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.6,.05))
plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.2,x1=.9,y0=.9,y1=.2,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="b.  Trade-off 1:",side=3,outer=FALSE,adj=0,line=1.6)
mtext(text="Seed count-reproductive costs",side=3,outer=FALSE,adj=0,line=0.7)
mtext(text="seed count,",side=2,line=1.3,outer=FALSE,cex=0.8)
mtext(text="scaled to plant size",side=2,line=0.4,outer=FALSE,cex=0.8)
mtext(text="reproductive costs",side=1,line=0.3,outer=FALSE,cex=0.8)
mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,cex=0.8)
#extra.top.left("b",2,1)

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.8,y0=.8,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="c.  Trade-off 2.",side=3,outer=FALSE,adj=0,line=1.6)
mtext(text="Ovule count-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
mtext(text="mature ovules count,",side=2,line=1.3,outer=FALSE,cex=0.8)
mtext(text="scaled to plant size",side=2,line=0.4,outer=FALSE,cex=0.8)
mtext(text="pollen attraction costs",side=1,line=0.3,outer=FALSE,cex=0.8)
mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,cex=0.8)
#extra.top.left("c",2,1)

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="d.  Trade-off 3.",side=3,outer=FALSE,adj=0,line=1.6)
mtext(text="Choosiness-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
mtext(text="choosiness",side=2,line=1.3,outer=FALSE,cex=0.8)
mtext(text="(ovule:seed)",side=2,line=0.4,outer=FALSE,cex=0.8)
mtext(text="pollen attraction costs,",side=1,line=0.3,outer=FALSE,cex=0.8)
mtext(text="scaled to plant size",side=1,line=1.2,outer=FALSE,cex=0.8)
mtext(text="(mg/seed)",side=1,line=2.1,outer=FALSE,cex=0.8)
#extra.top.left("d",2,1)
dev.off()

@@

>>>>

#DISCUSSION - slope of seed size vs repro costs not different from values reported in Lord; i.e. testing slope against the 1.1 she had.

slopes <- sma(repro_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1.1173,method="SMA", log="xy")

checking_slope <- dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)

@@

@@

#repro costs
slopes <- sma(repro_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")

@@

#accessory costs
slopes <- sma(accessory_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")

acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

#success costs
slopes <- sma(success_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")

acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

#pollen attraction costs
slopes <- sma(pollen_attract_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")

acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

#provisioning costs
slopes <- sma(provisioning_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")

acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

#discarded costs
slopes <- sma(discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")

acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

#discarded prepollen costs
slopes <- sma(prepollen_discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")

acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

#discarded postpollen costs
slopes <- sma(postpollen_aborted_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")

acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

acc_by_species$variable = c("total reproductive costs","total accessory costs","seed costs","pollen attraction costs","provisioning costs", "failed tissues costs","failed pre-pollination costs","failed provisioning costs")

@@

#Figure 01. predictions
```{r}
png("ms/Accessory/output/Figure01b&c&d_predictions.png", height=3.6, width=9, units="in", res=300)
par(mfrow=c(1,3), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.6,.05))
plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.2,x1=.9,y0=.9,y1=.2,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="Trade-off 1:",side=3,outer=FALSE,adj=0,line=1.6)
mtext(text="Seed count-reproductive costs",side=3,outer=FALSE,adj=0,line=0.7)
mtext(text="seed count,",side=2,line=1.3,outer=FALSE,cex=0.8)
mtext(text="scaled to plant size",side=2,line=0.4,outer=FALSE,cex=0.8)
mtext(text="reproductive costs",side=1,line=0.3,outer=FALSE,cex=0.8)
mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,cex=0.8)
#extra.top.left("b",2,1)

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.8,y0=.8,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="Trade-off 2.",side=3,outer=FALSE,adj=0,line=1.6)
mtext(text="Ovule count-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
mtext(text="mature ovules count,",side=2,line=1.3,outer=FALSE,cex=0.8)
mtext(text="scaled to plant size",side=2,line=0.4,outer=FALSE,cex=0.8)
mtext(text="pollen attraction costs",side=1,line=0.3,outer=FALSE,cex=0.8)
mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,cex=0.8)
#extra.top.left("c",2,1)

plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
mtext(text="Trade-off 3.",side=3,outer=FALSE,adj=0,line=1.6)
mtext(text="Choosiness-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
mtext(text="choosiness",side=2,line=1.3,outer=FALSE,cex=0.8)
mtext(text="(ovule:seed)",side=2,line=0.4,outer=FALSE,cex=0.8)
mtext(text="pollen attraction costs,",side=1,line=0.3,outer=FALSE,cex=0.8)
mtext(text="scaled to plant size",side=1,line=1.2,outer=FALSE,cex=0.8)
mtext(text="(mg/seed)",side=1,line=2.1,outer=FALSE,cex=0.8)
#extra.top.left("d",2,1)
dev.off()

@@

names(acc_slopes) <- c("species","n_propagule","r2_propagule","p_propagule","n_flower","r2_flower","p_flower")

### 2017-02-14 ms/Accessory/Wenk-Accessory-SI.Rnw
work on Accessory manuscript - Supplementary Information should currently compile. Tables should be final (other than sequence). Small amount more worked needed in descriptions at beginning.
next version of manuscript complete except very end of Intro

\clearpage
<<echo=FALSE, results='asis', warning=FALSE>>=
make_table_RA_shifts_with_age <- function() {
  xvar <- "repro_inv"
  yvar <- "accessory_per_seed"
  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

@@

  xvar <- "total_weight_0"
  yvar <- "accessory_per_seed"
  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

@@

  xvar <- "age"
  yvar <- "accessory_per_seed"
  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

@@

TableS16$species  <- paste("\\textit{",unique(TableS16$species),"}", sep="")
@

\begin{table}[H]
\centering
\caption{Shifts in accessory costs with shifts in age, plant size, or reproductive effort.}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
\hline
& \multicolumn{3}{c|}{Accessory costs} & \multicolumn{3}{c}{Accessory costs}& \multicolumn{3}{c}{Accessory costs} \\
& \multicolumn{3}{c|}{vs. RE} & \multicolumn{3}{c}{vs. plant mass (mg)}& \multicolumn{3}{c}{vs. age} \\
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS17)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight (mg) $\times$ bud count'}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
\hline
& \multicolumn{3}{c|}{Total reproductive investment} & \multicolumn{3}{c}{Total reproductive investment} \\
& \multicolumn{3}{c|}{vs. propagule investment} & \multicolumn{3}{c}{vs. flower investment} \\
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS16)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Count of buds initiated is well predicted by plant size}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}}
\hline
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS17)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

>>>>

\clearpage
<<echo=FALSE, results='asis', warning=FALSE>>=
make_table_RA_shifts_with_age <- function() {
  xvar <- "repro_inv"
  yvar <- "accessory_costs"
  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

@@

  xvar <- "total_weight_0"
  yvar <- "accessory_costs"
  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

@@

  xvar <- "age"
  yvar <- "accessory_costs"
  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

@@

@

\begin{table}[H]
\centering
\caption{Shifts in accessory costs with shifts in age, plant size, or reproductive effort.}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
\hline
& \multicolumn{3}{c|}{Accessory costs} & \multicolumn{3}{c}{Accessory costs}& \multicolumn{3}{c}{Accessory costs} \\
& \multicolumn{3}{c|}{vs. RE} & \multicolumn{3}{c}{vs. plant mass (mg)}& \multicolumn{3}{c}{vs. age} \\
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS16)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight (mg) $\times$ bud count'}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
\hline
& \multicolumn{3}{c|}{Total reproductive investment} & \multicolumn{3}{c}{Total reproductive investment} \\
& \multicolumn{3}{c|}{vs. propagule investment} & \multicolumn{3}{c}{vs. flower investment} \\
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS17)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Count of buds initiated is well predicted by plant size}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}}
\hline
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS18)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

<<echo=FALSE, results='asis', warning=FALSE>>=
make_table_Table2_using_propagule <- function() {
slopes <- sma(repro_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
acc_by_species <- dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)

slopes <- sma(accessory_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

slopes <- sma(success_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

slopes <- sma(pollen_attract_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

slopes <- sma(provisioning_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

slopes <- sma(discarded_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

slopes <- sma(prepollen_discarded_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

slopes <- sma(postpollen_aborted_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

acc_by_species$variable = c("total reproductive costs","total accessory costs","seed costs","pollen attraction costs","provisioning costs", "failed tissues costs","failed pre-pollination costs","failed provisioning costs")

acc_by_species$Slope <- format(acc_by_species$Slope,nsmall=2,digits=2)
acc_by_species$Slope_lowCI <- format(acc_by_species$Slope_lowCI,nsmall=2,digits=2)
acc_by_species$Slope_highCI <- format(acc_by_species$Slope_highCI,nsmall=2,digits=2)

acc_by_species$slope2 <- paste(acc_by_species$Slope," (",acc_by_species$Slope_lowCI," - ",acc_by_species$Slope_highCI,")",sep="")

acc_by_species$r2 <- format(acc_by_species$r2,digits=2)
acc_by_species$pval <- format_p(acc_by_species$pval)
acc_by_species$Slope_test_p <- format(acc_by_species$Slope_test_p,digits=2)
acc_slopes <- dplyr::select(acc_by_species,variable,r2,slope2,Slope_test_p)
}
TableS19 <- make_table_Table2_using_propagule()
@
\begin{table}[H]
\centering
\caption{Scaling of reproductive tissue costs with total propagule size}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.94cm}x{3cm}x{1.5cm}}
\hline
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS19)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}
